Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-01 PaperMagneticProfiles_JBSMSE.tex
Conclude reivision of introduction.

Magnetic refrigeration (MR) is an emerging cooling technology which does not rely on hazardous fluids. In MR, the temperature of a  \emph{magnetocaloric material} (MCM) changes as a result of cyclical changes in the applied magnetic field due to the so-called \emph{magnetocaloric effect} (MCE). The magnitude of the MCE depends on  material properties, magnetic field variation and temperature, and it is maximum at the Curie temperature of the material \cite{bib:smith-magneto, bib:kitanovski}. Applications of the MCE at near room-temperature are not restricted to cooling applications; it can also be applied to the development of thermomagnetic motors \cite{bib:kaneko}.

@@

For operating temperatures typical of household cooling applications, the MCE is of the order of \num{2}-\SI{5} K/T. To amplify this temperature change, heat regeneration is usually employed \cite{bib:kitanovski}. Active magnetic regenerators (AMR) are thermal devices in which the magnetocaloric material is packed as a porous matrix subjected to periodic flow of an aqueous heat transfer fluid. The flow is put in sync with successive magnetization and demagnetization steps of the MCM in the porous bed to produce a refrigerating effect. Thus, the AMR is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously to build up a longitudinal temperature profile in the matrix. The layers can be made of the same material, resulting in a homogeneous regenerator. However, given the dependence of the MCE on temperature, it is desirable to build \emph{multilayer} regenerators, where each adjacent layer has a slightly different composition that will function around its own Curie temperature, maximizing the magnetocaloric effect of each portion.

@@

Fluid flow profiles can be more easily investigated  experimentally, as no changes in the fluid flow hardware are required. In particular, the effect of the \emph{duration} of the fluid blows has been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}. There appears to be a consensus in the literature that the cooling capacity of magnetic refrigerators can be increased by displacing the fluid during periods where the magnetic field is at its extreme values.

In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in terms of their synchronization with the fluid flow profile. Considering a trapezoidal magnetic profile and a square fluid flow waveform, a numerical analysis showed that small delays between the increase of the magnetic field and the start of the fluid flow is beneficial for the cooling capacity, to assure the solid is fully magnetized before the fluid starts transfering energy from it \citet{bib:bjoerk11_amr}. If this delay is further increased so that the fluid flow period can coincide with diferent stages of the magnetic profile, different thermodynamic cycles can be obtained with different performance trends; the Brayton AMR cycle (explained previously) yields the highest cooling capacities, while the Ericsson AMR cycle (with isothermal (de)magnetization steps) yield the highest values of the coefficient of performance \cite{bib:plaznik13-numer}. This conclusion was confirmed by the more extensive numerical analysis of \cite{bib:kitanovski}, which also varied the amplitude of the trapezoidal magnetic profile and proposed magnetic circuit designs which could generate these profiles.

\colorbox{yellow}{acho q cabe explicar brevemente o que os trabalhos de \cite{TUSEK20111507} e \cite{bib:bjoerk11_amr} fizeram...}. Trevizoli et al.~\cite{bib:trevizoli16_perfor_model} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles. However, no systematic assessment of the effect of amplitude was performed nor did they investigate different geometries \colorbox{yellow}{nao estah claro o que vc quer dizer por geometries}.

\colorbox{yellow}{Fabio, acho que revisao bibliografica tem que ser expandida, trazendo trabalhos mais recentes em refrigeracao magnetica.}

\colorbox{yellow}{Tambem tem que trazer aqui para a revisao os nossos artigos que mediram/testaram/modelaram as valvulas.}

@@

The hydraulic system designed to modulate the fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations. The electrical power consumed by the valve array is computed separately from other work contributions. An application of electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}.

\colorbox{yellow}{Fabio, a ultima frase do paragrafo acima nao  cabe aqui... quero dizer que a aplicacao deveria ter sido discutida na revisao bibliografica, a qual precisa ser expandida}

>>>>

Magnetic refrigeration (MR) is an emerging cooling technology which does not rely on hazardous fluids. In MR, the temperature of a  \emph{magnetocaloric material} (MCM) changes as a result of cyclical changes in the applied magnetic field due to the so-called \emph{magnetocaloric effect} (MCE). The magnitude of the MCE depends on  material properties, magnetic field variation and temperature, and it is maximum at the Curie temperature of the material \cite{bib:smith-magneto, bib:kitanovski}. Applications of the MCE at near room-temperature are not restricted to cooling applications \cite{bib:gimaev19-review-htsc,bib:greco19}; it can also be applied to the development of thermomagnetic motors \cite{bib:kaneko19-desig}.

@@

For operating temperatures typical of household cooling applications, the MCE is of the order of \num{2}-\SI{5}{\kelvin\per\tesla}. To amplify this temperature change, heat regeneration is usually employed \cite{bib:kitanovski}. Active magnetic regenerators (AMR) are thermal devices in which the magnetocaloric material is packed as a porous matrix subjected to periodic flow of an aqueous heat transfer fluid. The flow is put in sync with successive magnetization and demagnetization steps of the MCM in the porous bed to produce a refrigerating effect. Thus, the AMR is essentially a cascade of infinitesimal ``layers'' of MCM that are activated simultaneously to build up a longitudinal temperature profile in the matrix. The layers can be made of the same material, resulting in a homogeneous regenerator. However, given the dependence of the MCE on temperature, it is desirable to build \emph{multilayer} regenerators, where each adjacent layer has a slightly different composition that will function around its own Curie temperature, maximizing the magnetocaloric effect of each portion.

@@

Fluid flow profiles can be more easily investigated  experimentally, as no changes in the fluid flow hardware are required, provided a reliable and flexible valving system is in place. In particular, the effect of the \emph{duration} of the fluid blows has been extensively investigated \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}. There appears to be a consensus in the literature that the cooling capacity of magnetic refrigerators can be increased by displacing the fluid during periods where the magnetic field is at its extreme values.

The control of these blow durations can be achieved with the use of solenoid valves; a model for a digital hydraulic system and a calculation of valve power has been presented by  \cite{bib:cardoso16_trans}, who showed that, if the opening and closing times are fast enough compared to the cycle period, then valve power is indepedent of frequency and proportional to the blow duration.  An application of  electronic valves in AMR devices has been presented by \cite{bib:nakashima18-perfor-asses-solen-valves-flow}, using the control logic (for synchronizing the valve operation with the magnetic profile) described by \cite{bib:hoffmann17-actuat}.

In contrast, because of the complexities involved in designing and fabricating magnetic circuits, the applied magnetic field profiles (or simply the magnetic waveforms) are much less studied, and are usually investigated in terms of their synchronization with the fluid flow profile with numerical investigations. Considering a trapezoidal magnetic profile and a square fluid flow waveform, a numerical analysis showed that small delays between the increase of the magnetic field and the start of the fluid flow is beneficial for the cooling capacity, to assure the solid is fully magnetized before the fluid starts transfering energy from it \cite{bib:bjoerk11_amr}. To the authors' knowledge, the only work that experimentally varied the magnetic profile, by controlling the rotation of magnetic cylinders, is the work by \cite{bib:benedict16_desig}, which also showed that cooling capacity of an AMR device is dependent on this lag between magnetization and fluid flow.

If this delay is further increased so that the fluid flow period can coincide with diferent stages of the magnetic profile, different thermodynamic cycles can be obtained with different performance trends; the Brayton AMR cycle (explained previously) yields the highest cooling capacities, while the Ericsson AMR cycle (with isothermal (de)magnetization steps) yield the highest values of the coefficient of performance \cite{bib:plaznik13-numer}. This conclusion was confirmed by the more extensive numerical analysis of \cite{bib:kitanovski}, which also varied the amplitude of the trapezoidal magnetic profile and proposed magnetic circuit designs which could generate these profiles.  Trevizoli et al.~\cite{bib:asme-mce} carried out a numerical comparison of the square wave (step change), sinusoidal and rectified cosine magnetic profiles for a sinusoidal fluid profile and concluded that the cooling capacity and maximum temperature spans are maximal for the instantaneous magnetic profile.

As previously noted, the fluid flow profile is implemented with proper design of the fluid flow system, while the magnetic profile is an important input when designing a magnetic circuit \cite{bib:oh13-air}. With the goal of AMR design, none of works reviewed in this section considered different \emph{shapes} and \emph{amplitudes} of the magnetic field waveform. Regarding shape, the combination of a trapezoidal magnetic profile and an instantaneous fluid flow profile is prevalent in the literature \cite{bib:bjoerk11_amr,bib:benedict16_desig,bib:park17-devel-k-k}, and this case is also investigated in the present paper. However, sinusoidal magnetic profiles can be achieved with more compact systems \cite{bib:trevizoli16_pump}, and their generation and impact of AMR devices have been investigated by  our group [PAPERS JMMM E TRADEOFF], but no work has investigated how these waveforms, when synchronized with optimized fluid flow profiles, can compare with the instantaneous magnetic profile, which the literature identifies as the optimal one when the fluid flow profile is fixed.

@@

The hydraulic system designed to modulate the fluid flow through different regenerators at different time instants is composed of a pump and a set of electronic valves which can be precisely controlled to yield the desired blow durations. The electrical power consumed by the valve array is computed separately from other work contributions.
